---
title: "File Input in R"
output:
  html_document:
    df_print: paged
---

Sometimes you will need to import a bunch of files into R. We don't want to do this manually, listing the path to each file. Instead, we can use tools in R to vectorize
this process.


# Setup and workflow

I highly recommend implementing R Studio projects into your workflow. By using R Studio projects, you contain individual projects within a single working directory. That way, you will not get mixed up when working on different projects simulteanously. Every time you start working on a project, open up the .Rproj file that R creates for you when you first create a new project. By doing this, a new instance of R Studio will load up with your the working directory associated with your R project.

In addition to R Studio projects, using the *here* library will help you navigate your files and directories easily from your project directory. The *here* library allows you to construct paths to your files and sub-directories by augmenting the path root. More on this below


```{r include=FALSE}
# load libraries
library(here)
library(tools)
```



```{r}
# your path root
here::here()



```

